\documentclass[10pt, letterpaper]{article}
\IfFileExists{cv/cv_common.tex}{\input{cv/cv_common.tex}}{\input{cv_common.tex}}

\begin{document}

\docHeader{Ph.D. student in Computer Science, RL / optimization theory}{-6pt}

\section{Research Interests}
\small{
I develop practical optimization algorithms with strong theoretical guarantees,
with a focus on online learning, bandits, and reinforcement learning. I am also
interested in statistical learning theory, fundamental limits in stochastic
optimization, and AI for math.
}

\section{Education}
\entry
{King Abdullah University of Science and Technology (KAUST)}{Dec. 2025 -- Present}
{Ph.D. Student in Computer Science}{Thuwal, Saudi Arabia}
\begin{itemize}
  \item Advisor: Francesco Orabona.
  \item Research focus: practical optimization algorithms with theoretical guarantees, online learning, bandits, reinforcement learning, statistical learning theory, and fundamental limits in stochastic optimization.
\end{itemize}

\entry
{King Abdullah University of Science and Technology (KAUST)}{Aug. 2024 -- Dec. 2025}
{M.Sc. in Computer Science}{Thuwal, Saudi Arabia}
\begin{itemize}
  \item Continued into the KAUST Computer Science Ph.D. program.
  \item Selected coursework: online learning, high-performance computing, numerical methods for stochastic differential equations, computing systems and concurrency.
\end{itemize}

\entry
{National Taiwan University}{Sep. 2012 -- Jan. 2018}
{B.Sc. in Computer Science, Minor in Mathematics}{Taipei, Taiwan}
\begin{itemize}
  \item Selected coursework: algorithm design and analysis, real analysis, abstract algebra, linear algebra, probability theory, numerical methods.
\end{itemize}

\section{Publications}
\paperLine
{\href{https://arxiv.org/abs/2606.24981}{A Single Stepsize Suffices for Unprojected Linear TD(0): Simultaneous Robust and Fast Rates via Polyak--Ruppert Averaging}}
{COLT 2026}
{\textbf{Wei-Cheng Lee}, Francesco Orabona.}

\paperLine
{\href{https://proceedings.mlr.press/v291/saad25a.html}{New Lower Bounds for Stochastic Non-Convex Optimization through Divergence Decomposition}}
{COLT 2025}
{El Mehdi Saad, \textbf{Wei-Cheng Lee}, Francesco Orabona.}

\paperLine
{\href{https://papers.nips.cc/paper_files/paper/2018/hash/09779bb7930c8a0a44360e12b538ae3c-Abstract.html}{MixLasso: Generalized Mixed Regression via Convex Atomic-Norm Regularization}}
{NeurIPS 2018}
{Ian E.H. Yen, \textbf{Wei-Cheng Lee}, Kai Zhong, Sung-En Chang, Pradeep Ravikumar, Shou-De Lin.}

\paperLine
{\href{https://proceedings.mlr.press/v70/yen17a.html}{Latent Feature Lasso}}
{ICML 2017}
{Ian E.H. Yen, \textbf{Wei-Cheng Lee}, Sung-En Chang, Arun S. Suggala, Shou-De Lin, Pradeep Ravikumar.}

\paperLine
{\href{https://arxiv.org/abs/2511.11211}{A Best-of-Both-Worlds Proof for Tsallis-INF without Fenchel Conjugates}}
{arXiv}
{\textbf{Wei-Cheng Lee}, Francesco Orabona.}

\paperLine
{\href{https://arxiv.org/abs/2506.01052}{A Robust $\widetilde{\mathcal{O}}(1/\sqrt{T})$ Rate for Unprojected TD Learning with Linear Function Approximation}}
{arXiv}
{\textbf{Wei-Cheng Lee}, Francesco Orabona.}

\section{Research Experience}
\entry
{Graduate Research, King Abdullah University of Science and Technology (KAUST)}{Aug. 2024 -- Present}
{M.Sc./Ph.D. Student in Computer Science}{Thuwal, Saudi Arabia}
\begin{itemize}
  \item Proved finite-time high-probability guarantees for unprojected linear TD(0) under Markovian sampling, showing that a single stepsize schedule yields bounded iterates and both robust curvature-free and fast curvature-dependent rates via Polyak--Ruppert averaging.
  \item Established query-complexity lower bounds for first-order stochastic non-convex optimization under structural conditions such as quasar-convexity, quadratic growth, and restricted secant inequalities, using divergence decomposition to reduce optimization to hard function-identification problems.
  \item Developed a simplified primal analysis for Tsallis-INF in multi-armed bandits that proves best-of-both-worlds guarantees via OCO tools instead of Fenchel-conjugate machinery.
\end{itemize}

\entry
{Institute of Information Science, Academia Sinica}{Feb. 2022 -- Mar. 2024}
{Research Assistant}{Taipei, Taiwan}
\begin{itemize}
  \item Proved regret guarantees for online reinforcement learning in infinite-horizon average-reward MDPs with full-information feedback, developing a new entropic-linear-program analysis for Hedge-style behavior across stochastic and adversarial regimes.
\end{itemize}

\entry
{Graduate Research, National Taiwan University}{Feb. 2018 -- Jun. 2021}
{M.Sc. Student}{Taipei, Taiwan}
\begin{itemize}
  \item Derived algorithms for log-loss function classes, with emphasis on online portfolio selection.
\end{itemize}

\section{Engineering Experience}
\entry
{Saudi Aramco, Research \& Development Center}{Jun. 2025 -- Jul. 2025}
{Graduate Intern}{Dhahran, Saudi Arabia}
\begin{itemize}
  \item Prototyped a Pyomo-based solver for gas-oil separation network optimization, formulating the problem as a mixed-integer nonlinear program and integrating JAX-accelerated derivative computations with finite-difference validation.
\end{itemize}

\entry
{Graduate Institute of Biomedical Electronics and Bioinformatics, NTU}{Aug. 2021 -- Jan. 2022}
{Research Assistant}{Taipei, Taiwan}
\begin{itemize}
  \item Contributed to a collaborative NTU-Far Eastern Memorial Hospital project on ICD-10 coding support, applying BERT-based language models to classify clinical case descriptions for Taiwan National Health Insurance workflows.
\end{itemize}

\section{Teaching}
\entry{Reinforcement Learning, KAUST}{Spring 2026, Spring 2025}{Teaching Assistant}{}
\par\vspace{2pt}
\entry{Optimization Algorithms, National Taiwan University}{Fall 2019, Fall 2018}{Teaching Assistant}{}
\par\vspace{2pt}
\entry{Probability, National Taiwan University}{Spring 2018, Spring 2015}{Teaching Assistant}{}

\section{Honors}
\entry
{Presidential Award, National Taiwan University}{Spring 2014, Fall 2012}
{Awarded to the top 5\% of students each semester}{}

\section{Technical Stack}
\small{
\textbf{Programming:} Python, JAX, PyTorch, C/C++, MATLAB, Julia, Go, JavaScript.
}

\end{document}
